HBCC - sgACC - FEATURECOUNTS - GRCh38 - CQN

### 2020-05-19 individual-cohorts/HBCC_sgACC_FEATURECOUNTS_GRCh38_CQN.Rmd
fix mvIC syntax

COVARIATES <- droplevels(COVARIATES)
# Stepwise regression
phase1 <- mvIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = base_formula,
                         data = bar,
                         variables = array(c("(1|Reported_Gender)", "scale(PMI)",
                                             "scale(ageOfDeath)", "scale(RIN)", "scale(RIN2)", "scale(EV.1)",
                                             "scale(EV.2)", "scale(EV.3)", "scale(EV.4)", "scale(EV.5)")))
kable(phase1$settings)
kable(phase1$trace)
as.character(phase1$formula)[2]
```

>>>>

# Stepwise regression
phase1 <- mvIC::mvForwardStepwise(exprObj = CQN.GENE_EXPRESSION$E,
                         baseFormula = base_formula,
                         data = COVARIATES,
                         variables = array(c("(1|Reported_Gender)", "scale(PMI)",
                                             "scale(ageOfDeath)", "scale(RIN)", "scale(RIN2)", "scale(EV.1)",
                                             "scale(EV.2)", "scale(EV.3)", "scale(EV.4)", "scale(EV.5)")))
kable(phase1$settings)
kable(phase1$trace)
as.character(phase1$formula)[2]
```
